Project assignment - Tahoe-LAFS with SHA-3 candidates

### 2010-12-14 paper/main.tex
Calculated cython overhead

>>>>

\section{Eliminating overhead in measurements}
The following measurements were done to eliminate the overhead introducer by
our work.

\paragraph{Cython bindings}
To eliminate as much as possible of overhead introduced by our bindings, we
timed the calls from our bindings to the underlying C-function. The overhead
should be the same for all bindings, since the Cython code is the same. The
measured overhead, calculated from BLAKE can be seen in Table XX.

\input{tables/cython_overhead}

\paragraph{Modification to Tahoe-\ac{LAFS}}
Because we write to two files after each hash calculation, this will create an
overhead in the measurements that would not normaly exist in Tahoe-\ac{LAFS}.
This overhead should be about the same for all candidates, since the number of
writes are equal. The results and calculations for this overhead, based on runs
with double \ac{SHA}-256 can be seen in Table XX.
